### 2025-09-25 paper/sec/evaluation.tex

How well do the generated expressions generalise when the underlying data changes, or when the input contains
misleading or ill-specified information? We test whether generated queries continue to produce correct outputs
under a set of hand-generated counterfactual modifications of the dataset, based on expected query results
specific to each test case, and also how counterfactual performance is impacted by the presence of misleading
or adversarial phrasing. able~\ref{tab:problematic_cases} shows some of cases which are ``problematic'' in
this sense; in these cases, producing a valid expression is likely to be challenging because of ambiguities in
the input data or accompanying natural language.

>>>>

How well do the generated expressions generalise when the underlying data changes, or when the input contains
misleading or ill-specified information? We test whether generated queries continue to produce correct outputs
under a set of hand-generated counterfactual modifications of the dataset, based on expected query results
specific to each test case, and also how counterfactual performance is impacted by the presence of misleading
or adversarial phrasing. Table~\ref{tab:problematic_cases} shows some of cases which are ``problematic'' in
this sense; in these cases, producing a valid expression is likely to be challenging because of ambiguities in
the input data or accompanying natural language.
